%------------------------------------
% JOB INFORMATION
%------------------------------------

\newcommand{\position}{[position]}
\newcommand{\company}{[company]}


%------------------------------------
% CONTACT INFORMATION
%------------------------------------

\newcommand{\name}{Mark Joslin}
\newcommand{\phone}{(517) 304-3745}
\newcommand{\location}{Brighton, MI}
\newcommand{\email}{mjoslin93@protonmail.com}
\newcommand{\github}{github.com/mjoslin-ai}
\newcommand{\linkedin}{linkedin.com/in/markjoslin-ai}


%------------------------------------
% SUMMARY
%------------------------------------

\newcommand{\summary}{Curious data enthusiast with a strong passion for analytics, problem-solving, and transforming complex data into actionable insights. Proven expertise in Python, SQL, data modeling, and visualization tools like PowerBI, demonstrated through previous work experience and personal projects. Eager to leverage my data specialist background to innovate, learn, and make a meaningful impact in a dynamic and growth-oriented environment.}


%------------------------------------
% SKILLS
%------------------------------------

\newcommand{\skillsCategoryZero}{Tools}
\newcommand{\skillsZero}{Python, R, SQL, DAX, Excel}

\newcommand{\skillsCategoryOne}{Visualization}
\newcommand{\skillsOne}{PowerBI, Matplotlib, ggplot2}

\newcommand{\skillsCategoryTwo}{Version control}
\newcommand{\skillsTwo}{GitHub, Azure DevOps}


%------------------------------------
% EXPERIENCE
%------------------------------------

\newcommand{\expTitleZero}{Data Specialist (Remote)}
\newcommand{\expCompanyZero}{\href{https://www.gcaps.net/}{GCAPS} | {Alton, VA}}
\newcommand{\expStartZero}{4/2021}
\newcommand{\expEndZero}{5/2024}
\newcommand{\expResponsibilitiesZero}{
\item Performed literature reviews for NHTSA in areas such as AI in ADAS/ADS and traffic simulation tools to help them better understand perception stack models and other technologies.
\item Maintained an internal website and SQL database hosted on Azure to track driving simulation construction used across a diverse team to enhance workflow and quantify completion rate.
\item Created digital reconstructions of crash and near crash scenarios with the use of RoadRunner and Excel using VTTI’s database to allow subscribers means to study these scenarios under different factors such as sensor degradation and misinformation.
\item Developed a Python script for dimensionality reduction and clustering of highway cut-in and lane change maneuvers using VTTI’s naturalistic driving database, visualizing and analyzing factors’ central tendencies to enhance the Division of Data and Analytics’ understanding of these maneuvers compared to domain knowledge.}

\newcommand{\expTitleOne}{Cataloging Intern}
\newcommand{\expCompanyOne}{\href{https://www.ams.org/publications/math-reviews/math-reviews}{American Mathematical Society} | {Ann Arbor, MI}}
\newcommand{\expStartOne}{5/2019}
\newcommand{\expEndOne}{8/2019}
\newcommand{\expResponsibilitiesOne}{
\item Queried a large database for institution codes for authors in submitted journals.
\item Prepared journals for storage in a separate database to allow subscribers access to the latest publications.
\item Assisted in author notifications regarding missing journal information such as lacking institution(s).}

\newcommand{\expTitleTwo}{Durability Driver}
\newcommand{\expCompanyTwo}{\href{https://www.chelseaprovinggrounds.com/en-us/Pages/Home.aspx}{Stellantis} | {Chelsea, MI}}
\newcommand{\expStartTwo}{5/2016}
\newcommand{\expEndTwo}{9/2017}
\newcommand{\expResponsibilitiesTwo}{
\item Conducted endurance tests identifying critical safety and performance issues to enhance vehicle reliability.
\item Issue documentation via Ipad to ensure precise diagnostics for the engineering team.
\item Maintained strict testing protocols such as oval track for power train, high hill grade and off road for four wheel drive, and specially designed roads for suspension.}


%------------------------------------
% EDUCATION
%------------------------------------

\newcommand{\eduDegreeZero}{Bachelor of Science in Data Science}
\newcommand{\eduInstitutionZero}{\href{https://wmich.edu/}{Western Michigan University} | {Kalamazoo, MI}}
\newcommand{\eduGradZero}{12/2020}

\newcommand{\eduDegreeOne}{Associate of Science in Engineering}
\newcommand{\eduInstitutionOne}{\href{https://www.schoolcraft.edu/}{Schoolcraft College} | {Livonia, MI}}
\newcommand{\eduGradOne}{5/2016}


%------------------------------------
% PROJECTS
%------------------------------------

\newcommand{\projDateZero}{8/2025}
\newcommand{\projTitleZero}{Coffee Sales Dashboard}
\newcommand{\projSourceZero}{\href{https://github.com/mjoslin-ai/Excel-Coffee_Sales_Dashboard}{GitHub}}
\newcommand{\projDetailsZero}{
\item Built an Excel dashboard to analyze coffee sales (2019–2022), tracking trends by coffee type, roast, country, and loyalty program using XLOOKUP, INDEX MATCH, pivot tables, charts, and slicers.
\item Provided insights into sales trends, seasonal patterns, and top customers/regions to support inventory and marketing strategies.}

\newcommand{\projDateOne}{10/2024}
\newcommand{\projTitleOne}{HR Analytics Dashboard}
\newcommand{\projSourceOne}{\href{https://github.com/mjoslin-ai/PowerBI-HR_Dashboard}{GitHub}}
\newcommand{\projDetailsOne}{
\item Developed a PowerBI dashboard to analyze working preference of employees between work from home and work from office along with sick leave percentage on a daily and monthly basis.
\item The report will help an employer when scheduling in-person meetings, product rollouts, and employee wellness.}


%------------------------------------
% REFERENCES
%------------------------------------

\newcommand{\refNameZero}{Alex Hatchett}
\newcommand{\refPositionZero}{Research Project Manager, GCAPS}
\newcommand{\refEmailZero}{\href{mailto:ahatchett@gcaps.net}{ahatchett@gcaps.net}}
\newcommand{\refPhoneZero}{(434) 766-6644}

\newcommand{\refNameOne}{Travis Terry}
\newcommand{\refPositionOne}{Research Scientist, GCAPS}
\newcommand{\refEmailOne}{\href{mailto:tterry@gcaps.net}{tterry@gcaps.net}}
\newcommand{\refPhoneOne}{(276) 780-0534}



