\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. Compile with XeLaTeX or LuaLaTeX to use academicons.

% Page layout 
\geometry{left=0.5in,right=3.5in,marginparwidth=2.5in,marginparsep=0.5in,top=0.5in,bottom=0.5in}

% Change the font depending on pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
  
  \usepackage[utf8]{inputenc}
    \usepackage{xcolor}
    \usepackage{graphicx}
    \usepackage{tikz}
\fi

% Colours 
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\definecolor{Maroon}{HTML}{771624}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Header
\begin{document}
\name{Mark Joslin}
\tagline{Data Specialist}

\personalinfo{%
  % Not all of these are required!
  % Add more with \printinfo{symbol}{detail}
  \email{mjoslin93@protonmail.com}
  \phone{517.304.3745}
  \location{Brighton, MI}
  \github{github.com/mjoslin-ai}
}

%% Make the header extend all the way to the right
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% File name containing the sidebar contents as an optional parameter to \cvsection.
\cvsection[resumeSidebar]{Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvevent{Data Specialist (Remote)}{Global Center for Automotive Performance Simulation (GCAPS)}{Apr '21 -- May '24}{Alton, VA}
\begin{itemize}
\item Performed literature reviews for the National Highway Traffic Safety Administration (NHTSA) and others in areas such as AI uses in ADAS/ADS, traffic simulation tools, and medical data cybersecurity. 
\smallskip
\item Maintained an internal website and SQL database to track naturalistic driving simulation construction. 
\smallskip
\item Created digital reconstructions of crash and near crash scenarios for customers who subscribe to Virginia Tech Transportation Institute's (VTTI's) large database of naturalistic driving.
\end{itemize}

\divider

\cvevent{Cataloging Intern}{American Mathematical Society}{May '19 -- Aug '19}{Ann Arbor, MI}
\begin{itemize}
\item Queried a large database for institution codes for each author in submitted journals.
\smallskip
\item Prepared journals to be stored in a database and 
accessed by our clients. 
\smallskip
\item Notified others to contact an author when key journal information is missing.
\end{itemize}

\divider

\cvevent{Durability Driver (Temporary)}{Stellantis}{May '16 -- Sep '17}{Chelsea, MI}
\begin{itemize}
\item Conducted rigorous endurance tests, identifying critical safety and performance issues pre- and post-launch.
\smallskip
\item Ensured precise diagnostics and issue documentation, streamlining engineering fixes.
\smallskip
\item Maintained strict testing protocols, enhancing vehicle reliability and validation efficiency.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Projects
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Projects}
\cvevent{Lane Change Exploratory Analysis}{Python}{}{}
\begin{itemize}
%\item Conducted exploratory data analysis into cut-in and lane change of naturalistic driving highway data and presented findings to Division of Data and Analytics at Virginia Tech Transportation Institute (VTTI).
\item Created a script that performs dimensionality reduction and clustering on highway cut-in and lane change maneuvers with VTTI's naturalistic driving database. Visualized and described each factor's central tendency across clusters.
\item The analysis helped the Division of Data and Analytics at VTTI better understand factors that affect these maneuvers compared to domain knowledge.
\end{itemize}

\divider

\cvevent{HR Analytics}{PowerBI}{}{}
\begin{itemize}
\item Developed a dashboard to analyze working preference of employees between work from home and work from office along with sick leave percentage on a daily and monthly basis.
\item The report will help an employer when scheduling in-person meetings, product rollouts, and employee wellness.
\end{itemize}

\clearpage

\end{document}
