\documentclass[10pt]{../cv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
\usepackage{lipsum}  
\input{../macros.tex} % For contact info data

% Suppress layout warnings
\hbadness=10000  % Suppresses warnings for bad horizontal spacing
\vbadness=10000  % Suppresses warnings for bad vertical spacing

\begin{document}


%---------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%---------------------------------------------------------------

\cvHeader{\name}{\designation}{\phone}{\location}{\email}{\github}{\linkedin}
\vspace{\baselineskip}

%---------------------------------------------------------------
%	Letter
%---------------------------------------------------------------

Dear Hiring Manager,
\\
\\
I am excited to apply for the [position] position at [company]. My passion for leveraging data to uncover meaningful insights began during my undergraduate studies when I discovered the field of data science. The opportunity to collaborate with professionals dedicated to [in about page] aligns with my enthusiasm for [passion]. [company]’s focus on community empowerment and innovation makes this role particularly appealing to me.
\\
\\
During my time at the Global Center for Automotive Performance Simulation (GCAPS), I gained valuable experience working with Virginia Tech Transportation Institute’s (VTTI’s) naturalistic driving data (NDD). I conducted database management and exploratory analysis on highway cut-in and lane change maneuvers, updating and maintaining the SQL database to document how simulation-based scenarios are constructed from the NDD. Additionally, I developed a website that allowed users to easily interact with and visualize progress toward completion. Beyond SQL, I honed my analytical problem-solving skills through a lane change exploratory analysis using Python. This analysis provided the Division of Data and Analytics at VTTI with enhanced insights into the factors affecting these maneuvers, expanding conventional domain knowledge. As a [position], I would bring these skills to [job responsibility].
\\
\\
One of the most compelling aspects of this role at [company] is the opportunity to pursue a career as a [career goal]. In my spare time, I actively educate myself on various aspects of personal finance, from cash alternatives to current market conditions—subjects that closely align with Lake Trust’s mission to support all aspects of its members’ well-being. Additionally, my family has strong ties to Lake Trust and holds the institution in the highest regard, not only in pursuing their own financial goals but also in supporting the community.
\\
\\
Thank you for your time and consideration. I look forward to learning more about the [position] at [company].
\\
\\
Sincerely,
\\
Mark Joslin


\end{document}