\documentclass[10pt]{../cv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
\usepackage{lipsum}  
\input{../macros.tex} % For contact info data

% Suppress layout warnings
\hbadness=10000  % Suppresses warnings for bad horizontal spacing
\vbadness=10000  % Suppresses warnings for bad vertical spacing

\begin{document}


%------------------------------------
%	TITLE AND CONTACT INFORMATION
%------------------------------------

\cvHeader{\name}{\phone}{\location}{\email}{\github}{\linkedin}
\vspace{\baselineskip}

%------------------------------------
%	Letter
%------------------------------------

Dear Hiring Manager,
\\
\\
I am excited to apply for the \position{} position at \company{}. My passion for leveraging data to uncover meaningful insights began during my undergraduate studies when I discovered the field of data science. The crossroads between equipping others to provide the best healthcare and the opportunity to learn and grow in the financial analysis and business intelligence space makes this role particularly appealing to me.
\\
\\
During my time at the Global Center for Automotive Performance Simulation (GCAPS), I gained valuable experience working with Virginia Tech Transportation Institute’s (VTTI’s) naturalistic driving data (NDD). I conducted exploratory analysis on highway cut-in and lane change maneuvers, providing the Division of Data and Analytics at VTTI with enhanced insights into the factors affecting these maneuvers, expanding conventional domain knowledge. I also maintained an internal database and developed an interactive website supporting the simulation team’s virtual reconstruction of the NDD — a resource that enhanced their daily workflow. I also presented an ideation project that steered GCAPS into the healthcare space by using our virtual simulation process on emergency room procedures that led to research papers on topics such as PII and PHI. As a \position{}, I would apply these technical and analytical skills—paired with a strong commitment to learning the nuances of finance—to effectively support the accounting department’s operations and decision-making.
\\
\\
I recognize that my employment history includes a gap attributable to health-related matters; nevertheless, I am eager to contribute meaningfully at \company{}. In my personal time, I proactively expand my knowledge of finance, encompassing macroeconomics, individual equities, and cryptocurrencies—a commitment to lifelong learning that is invaluable in a finance-oriented position. Furthermore, my personal experiences have underscored the critical importance of health, inspiring me to support health and wellness professionals by equipping them with essential tools for success.
\\
\\
Thank you for your time and consideration. I look forward to learning more about the \position{} position at \company{}.
\\
\\
Sincerely,
\\
Mark Joslin
\\
\\

%I am excited to apply for the Retirement Plan Specialist position at Guidant Financial. My passion for leveraging data to uncover meaningful insights began during my undergraduate studies when I discovered the field of data science. At the Global Center for Automotive Performance Simulation (GCAPS), I gained valuable experience working with naturalistic driving data (NDD) from the Virginia Tech Transportation Institute (VTTI). I conducted exploratory analysis on highway cut-in and lane change maneuvers, delivering enhanced insights into the factors affecting these maneuvers and expanding conventional domain knowledge for VTTI’s Division of Data and Analytics. I also maintained an internal database and developed an interactive website to support the simulation team’s virtual reconstruction of the NDD, enhancing their daily workflow. In a Retirement Plan Specialist role, I would bring my problem-solving skills, attention to detail, and passion for learning all things finance to support and educate Guidant Financial’s clients effectively.


\end{document}